Incremental tactics

### 2012-05-29 doc/papers/LFMTP2012/paper.tex
paper

\section{Background}
%% It’s an unsolved problem (1 page)

\paragraph{Motivational example}

@@

\section{Here is my idea}
%% Here is my idea (2 pages)

>>>>

\section{Use case}
%% It’s an unsolved problem (1 page)

\paragraph{A backend for incremental type checking}

@@

\paragraph{A language to write incremental type-checkers}

A few days earlier, the teacher is preparing the tool for the students
to train composing System \sysname{T} programs. He (or she) provides
the abstract syntax, the typing rules and the typing algorithm in
order to build the incremental type checker. How should he write the
algorithm? Usually, it takes a program and an environment and returns
nothing but we know that we want to return a derivation, and take
advantage of a higher-order representation of the syntax, so it
shouldn't be necessary to thread any explicit environment. %TODO
$$

$$
\section{Here is my idea}
%% Here is my idea (2 pages)
